Innovations Report: Procedural Fur System

### 2018-03-01 docs/paper.tex
progress on docs

\subsection{Existing Solutions} \label{sec:existing}
Existing Solutions.

@@

>>>>

\subsection{Existing Solutions} \label{sec:existing}
Existing Solutions. (Xgen, houdini)

@@

\subsection{Design} \label{sec:design}
From looking at existing fur systems I was able determine that my simplified fur system would need to consist of the following components:
\begin{itemize}
	\item Distributors - These are responsible for the distribution of curves onto user specified geometry. User controllable parameters could include density (curve count), distribution pattern (random, uniform), and curve length. These parameters could potentially be controlled by texture inputs.
	\item Operators - These are responsible for manipulation of the curves to achieve the desired look. Example operators could provide bending, clumping, or randomisation of input curves.
	\item Renderers - These are responsible for the rendering of curves into the application viewport. Example renderers could provide mesh, cuves as lines, or curves as ribbons rendering functionality. User controllable parameters could provide controls for the shading model in use, as well as control of the base and tip widths when rendering curve ribbons for example.
\end{itemize}
